### 2019-12-13 README.Rmd
updated to final reviewer revisions

The previously published model was found to contain a methodological flaw and to be spuriously precise. It greatly underestimated the impact of ending school-age vaccination compared to our updated, corrected, model. The model produced predictions with wide confidence intervals when parameter uncertainty was included. Model estimates were most comparable to notification data when an annual decrease in TB incidence rates of 1.9% was used. Using this assumption, we estimate that 1600 (2.5,97.5% Quantiles (Q): 1300, 2000) vaccines would have been required to prevent a single notification in 2004.

>>>>

The previously published model was found to contain a methodological flaw and to be spuriously precise. It greatly underestimated the impact of ending school-age vaccination compared to our updated, corrected, model. The updated model produced predictions with wide confidence intervals when parameter uncertainty was included. Model estimates based on an assumption of an annual decrease in TB incidence rates of 1.9% were closest to those estimated using notification data. Using this assumption, we estimate that 1600 (2.5,97.5% Quantiles (Q): 1300, 2000) vaccines would have been required to prevent a single notification in 2004.
